Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-12 paper.tex
Add discussion of wake recovery calculations, blockage; resolves #59

Results from the terms available (i.e. excluding $\partial / \partial x$) from
the right hand sides of Equations~\ref{eq:momentum} and \ref{eq:K-full} are
plotted in Figures~\ref{fig:mom-bar-graph} and \ref{fig:K-bar-graph},
respectively. We note that similar to \cite{Bachant2015-JoT}, the vertical
advection at this point in the wake is the dominant contributor to positive wake
recovery, caused by the unique vortex pattern created by the blade tips and
wakes.

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.9\textwidth]{figures/mom_bar_graph}
\caption{Momentum transport quantities.}
\label{fig:mom-bar-graph}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.9\textwidth]{figures/K_trans_bar_graph}
\caption{Mean kinetic energy transport quantities.}
\label{fig:K-bar-graph}
\end{figure}

>>>>

Results from the terms available (i.e. excluding $\partial / \partial x$) from
the right hand sides of Equations~\ref{eq:momentum} and \ref{eq:K-full} are
plotted in Figures~\ref{fig:mom-bar-graph} and \ref{fig:K-bar-graph},
respectively. Derivatives were computed using a second order finite difference
scheme, with central differencing for interior points, and inward facing schemes
for the boundaries. A weighted average for each term was then calculated based
on the grid spacing. We note that similar to \cite{Bachant2015-JoT}, the
vertical advection at this point in the wake is the dominant contributor to
positive wake recovery, caused by the unique vortex pattern created by the blade
tips and wakes.

@@

Transport due to cross-stream advection appears to become more negative at
higher $Re$. This could be a consequence of increasing free surface deformation
(higher $Fr$), which then decreases the effective flow cross-sectional area
downstream of the turbine, forcing more flow to accelerate around the sides of
the turbine.

    \includegraphics[width=0.9\textwidth]{figures/mom_bar_graph}

    \caption{Normalized momentum transport quantities computed as weighted
        averages from Equation~\ref{eq:momentum}.}

    \label{fig:mom-bar-graph}
\end{figure}

    \includegraphics[width=0.9\textwidth]{figures/K_trans_bar_graph}

    \caption{Normalized mean kinetic energy transport quantities computed as
        weighted averages based on Equation~\ref{eq:K-full}. Note that directions of
        the turbulent transport terms refer to the directions of their partial
        derivatives.}

    \label{fig:K-bar-graph}
\end{figure}
